\plaintitle

### 2025-05-21 docs/style/article-body.tex

\begin{tabular}{|c|c|c|} \hline \textbf{Bit size} &
\multicolumn{1}{c|}{\textbf{Teensy ($\mu s$)}} &
\multicolumn{1}{c|}{\textbf{Pico ($\mu s$)}} \\ \hline 64 & 13.1564 & 106.3914
\\ 512 & 788.3139 & 5302.4979 \\ 1024 & 3124.0580 & 21111.2163 \\ \hline
\caption{A brief overview of the testscript architecture.} \label{tab:iter1}

\end{tabular}

@@

\begin{tabular}{|c|c|} \hline \textbf{Bit size} &
\multicolumn{1}{c|}{\textbf{Avg ($\mu s$)}} \\ \hline 64/64 & 43.0760 \\ 512/512
& 2663.8194 \\ 1024/1024 & 10513.1767 \\ \hline \end{tabular}

\label{tab:iter3}

>>>>

\textbackslash begin\{table\}{[}ht{]}begin\{tabular\}\{\textbar c\textbar c\textbar c\textbar\} \hline \textbf{Bit size} \& \multicolumn{1}{c|}{\textbf{Teensy ($\mu s$)}} \& \multicolumn{1}{c|}{\textbf{Pico ($\mu s$)}} \textbackslash{} \hline 64 \& 13.1564 \& 106.3914 \textbackslash{} 512 \& 788.3139 \& 5302.4979 \textbackslash{} 1024 \& 3124.0580 \& 21111.2163 \textbackslash{} \hline

\caption{A brief overview of the testscript architecture.} \label{tab:iter1}

\textbackslash end\{tabular\} \label{tab:iter1}/end\{table\}

@@

\begin{table}[ht]\begin{tabular}{|c|c|} \hline \textbf{Bit size} &
\multicolumn{1}{c|}{\textbf{Avg ($\mu s$)}} \\ \hline 64/64 & 43.0760 \\ 512/512
& 2663.8194 \\ 1024/1024 & 10513.1767 \\ \hline \end{tabular}
\label{tab:iter3}\end{table}
